Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-20 paper/current/main.tex
edit and add s_i factors plot

>>>>

%
% Figure - s_i by factors
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/si_factors.pdf}
	\caption{
		\textbf{Factors relating to $s_{i}$ among universities}
		Correlation between various organization-level factors for U.S. universities and the value $s_{i}$.
		Dots correspond to organizations.	
		The red line is the line of  the best fit. 
		Red text is the regression estimate.
		Number of authors is the average annual count of unique mobile and non-mobile authors.
		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities. 
		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted. 
	}
	\label{fig:supp:semaxis_states}
\end{figure}
